\documentclass[12pt]{article}

\begin{document}

% Salutation
\noindent
Dear Mitacs Globalink selection committee,

%  When did you supervise the proposed candidate, and how many other students have you supervised at the same level? DONE

% Relative to the other students you have supervised at the same level, how productive was the proposed candidate while under your supervision (publications, contributions, etc.)?

% If possible, please comment on the productivity of the proposed candidate, relative to other researchers or students you have known at the same career stage.

% Are there any outstanding achievements (high-impact research results, awards, etc.) by the proposed candidate that you would like to further comment on?

% INTRODUCTION / WHO
\bigskip
\noindent
It is my pleasure to recommend Mr. \textbf{Russel Shawn Dsouza} for the Mitacs Globalink Internship 2020. Russel is currently in the third year of his undergraduate degree and is one of the most outstanding undergrads to intern at my lab. I encourage you to give him your most careful consideration. % main stuff - check again

\medskip
\noindent
I was Russel's research supervisor for his summer internship project from May to July of 2019 and the instructor for fourth semester course on Digital Signal Processing.
During that time, I have watched him grow into an outstanding individual who excels in both his academic and personal pursuits. % check again

%STAR for research internship
\medskip
\noindent
As a research intern, Russel worked on using Deep Convolutional Neural Networks Segmentation of nuclei in H\&E stained histopathology images of kidney tissues to improve automated diagnosis of cancer. He applied state of the art image processing techniques on the images in MATLAB to compare against deep learning.
Using PyTorch and Python, he coded a deep learning pipeline and built multiple fully convolutional networks. 
He also setup a complex CUDA-conda environment in Linux and trained the models locally on GPUs. %change

% some personal projects
\medskip
\noindent
He has also worked on using Natural Language Processing to classify fake news and using Deep Learning to identify Ponzi schemes in his free time using the GPUs in my lab.
% skills observed
He is capable of working independently with minimum guidance and support.

% get correct number
\medskip
\noindent
He has fit in well within my research group which has 3 PhD, 4 research assistants, 10 graduates and 4 undergraduates. % may remove

% interests and some hobbies under dr.
\medskip
\noindent
Russel is a promising student who shows serious enthusiasm in academics and ...
He was a member of IRIS, the official student-faculty-administration portal of NITK used by more than five thousand people every day. % can be better

\medskip
\noindent
He has an immense interest in the fields of Computer Vision, Computational Neuroscience, and Robotics. He is currently working on multiple projects related to each domain to further his understanding and expertise. % add or subtract as needed

\medskip
\noindent
In closing, I strongly recommend Russel for the summer internship research program offered by your esteemed organisation. % may change

\end{document}
