\documentclass[12pt]{article}
\usepackage[a4paper, total={6in, 9in}]{geometry}
\thispagestyle{empty}

\begin{document}
  \noindent
  Dear Mitacs Globalink selection committee,

  \bigskip
  \noindent
  It is my pleasure to recommend Mr. \textbf{Russel Shawn Dsouza} for the Mitacs Globalink Internship 2020. Russel is currently in the third year of his undergraduate degree and is one of the most outstanding undergraduates to intern in my lab. I encourage you to give him your most careful consideration.

  \medskip
  \noindent
  I was Russel's research supervisor for his summer internship project from May to July of 2019 and his instructor for the course on Digital Signal Processing.
  During that time, I have watched him grow into an outstanding individual who excels in both his academic and personal pursuits.

  \medskip
  \noindent
  As a research intern, Russel worked on using deep convolutional neural networks for segmentation of nuclei in H\&E stained histopathology images of kidney tissues to improve automated diagnosis of cancer.
  Using PyTorch, torchvision and scikit-learn, he built a deep learning pipeline and multiple fully convolutional neural networks and trained each model locally on GPUs. 
  He was able to setup a complex CUDA-conda environment in Linux.
  He also applied state of the art image processing techniques on the images in MATLAB and compared the results of classical techniques with that of deep learning methods.

  \medskip
  \noindent
  He has worked on using natural language processing to detect fake news and using deep learning to analyse Ethereum smart contracts in his spare time using the GPUs in my lab.
  He is capable of working independently with minimum guidance and support. 
  As a member of IRIS, the official student-faculty-administration portal of NITK, he has worked in a team of 30 students across disciplines for more than 9 months.
  He has fit in well within my research group which has 5 PhDs, 4 graduates and 4 undergraduates.
  He has shown an immense interest in the fields of Computer Vision, Computational Neuroscience, and Robotics and is working on multiple projects related to each domain to further his understanding and expertise.

  \medskip
  \noindent
  In closing, I strongly recommend Russel for the summer internship research program offered by your esteemed organisation. He has my strongest recommendation.
\end{document}
