\documentclass[margin]{res}

% Packages
\usepackage[pdftex,
            pdfauthor={Russel Shawn Dsouza},
            pdftitle={Russel Dsouza's Resume},
            pdfsubject={Resume},
            pdfkeywords={medical-imaging, computer-vision, deep-learning, neuroscience},
            pdfproducer={LaTeX},
            pdfcreator={pdflatex},
            colorlinks=true,
            linkcolor=blue,
            urlcolor =blue,
            citecolor=blue,
            anchorcolor=blue]{hyperref} % For URLs
\usepackage{xcolor} % For colors
\usepackage{fontawesome} % For icons

% Custom constants
\textheight=700pt % Increase text height

\begin{document}

  %	Personal information
  \name{Russel Shawn Dsouza}
  \address{National Institute of Technology\\
           Karnataka, India\\
           russel.171ec143@nitk.edu.in}
  \address{{\faMobile} (91+) 9611212081\\
           {\faLinkedin} \href{https://linkedin.com/in/rshwndsz}{linkedin.com/in/rshwndsz}\\
           {\faGithub} \href{https://github.com/rshwndsz}{github.com/rshwndsz}}


  \begin{resume}
    %	Education
    \section{Education}
      \textbf{National Institute of Technology Karnataka}, India\hfill
      2017-2021 \\
      {\sl B.Tech in Electronics and Communications Engineering}
      \hfill{CGPA: 8.7}

      \textbf{Little Rock Indian School}, Karnataka, India\hfill
      2004-2017 \\
      {\sl K-12}


    %	Projects
    \section{Notable Projects}
      \par
      \textbf{Computational Histopathology}\\
      Worked on implementing convolutional encoder-decoder architectures in PyTorch to perform the segmentation of nuclei in H\&E stained histopathology images of kidney tissues.

      \par
      \textbf{Detecting Ponzi schemes in Ethereum smart-contracts}\\
      Used a semi-supervised learning based model, built using PyTorch and torchtext, on raw bytecode of Ethereum smart contracts mined using Google BigQuery, to detect Ponzi schemes.

      \par
      \textbf{Detecting fake news using deep learning}\\
      Built a classifier using PyTorch and torchtext to identify the truth level of news articles from human verified facts and statements.

      \par
      \textbf{Face detection and recognition}\\
      Implemented real-time face detection and recognition using OpenCV, scikit-learn and dlib on a Raspberry Pi.


    %	Technical Skills
    \section{Technical Skills}
      \textbf{Languages}: Python, MATLAB, C, Rust, JavaScript, C++, Verilog
      \\
      \textbf{Frameworks/Libraries}: PyTorch, Keras, torchvision, scikit-learn, OpenCV
      \\
      \textbf{Web development}: Django, ExpressJS, ReactJS, GatsbyJS, GraphQL
      \\
      \textbf{Tools}: git, Docker, Linux, Google BigQuery, Xilinx Vivado, \LaTeX
      \\
      \textbf{Hardware}: Xilinx Artix 7 FPGA, Arduino, Raspberry Pi


    %	Experience
    \begin{format}
      \title{l}\dates{r}\\
      \employer{l}\location{r}\\
      \body\\
    \end{format}

    \section{Experience}
      \employer{\textcolor{black!80}{\small{under Dr. Shyam Lal, NITK}}}
      \location{\textcolor{black!80}{\small{Karnataka, India}}}
      \dates{\textcolor{black!80}{\small{Dec 2019 - Present}}}
      \title{\textbf{Winter Research Intern}}
      \begin{position}
        Working on the design and development of an automated kidney cancer detection system from H\&E stained histopathology images.
      \end{position}

      \employer{\textcolor{black!80}{\small{under Dr. Shyam Lal, NITK}}}
      \location{\textcolor{black!80}{\small{Karnataka, India}}}
      \dates{\textcolor{black!80}{\small{May 2019 - July 2019}}}
      \title{\textbf{Summer Research Intern}}
      \begin{position}
          Worked on reproducing state-of-the-art deep learning architectures for the segmentation of H\&E stained histopathology images of kidney tissues.
      \end{position}

      \employer{\textcolor{black!80}{\textcolor{black!80}{\small{IRIS, NITK}}}}
      \location{\textcolor{black!80}{\textcolor{black!80}{\small{Karnataka, India}}}}
      \dates{\textcolor{black!80}{\textcolor{black!80}{\small{August 2018 - April 2019}}}}
      \title{\textbf{Frontend Developer}}
      \begin{position}
        Worked on building the frontend for the official student management portal `IRIS' with more than five thousand daily active users including students, faculty, administrators and alumni.
        Mentored a freshman intern on frontend testing.
      \end{position}

      \employer{\textcolor{black!80}{\small{Pinnacle Media, Manipal, India}}}
      \location{\textcolor{black!80}{\small{Karnataka, India}}}
      \dates{\textcolor{black!80}{\small{May 2018 - July 2018}}}
      \title{\textbf{Python Developer}}
      \begin{position}
        Worked on implementing real-time face detection and recognition using OpenCV, dlib and scikit-learn on Raspberry Pi
      \end{position}


    %	Interests
    \section{Interests}
      Medical imaging, computer vision, computational neuroscience and augmented reality

  \end{resume}
\end{document}
